Inference using context-dependent models of mutation

### 2021-10-15 writeups/context-dependence.tex
a little fix and a hint

\begin{proof}
    First note that $\P\{X > kw\} \le \P\{N > k\}$.
    Now, use the fact that if $f(n) = n (n-1) \cdots (n-k) / (k+1)!$
    then $f(n) = 0$ for integers $0 \le n \le k$ and $f(n) \ge 1$ for $n > k$,
    and so $\P\{N > k\} \le \E[f(N)] = \lambda^{k+1} / k!$.
\end{proof}

>>>>

\begin{proof}
    First note that $\P\{X > kw\} \le \P\{N > k\}$.
    Now, use the fact that if $f(n) = n (n-1) \cdots (n-k) / (k+1)!$
    then $f(n) = 0$ for integers $0 \le n \le k$ and $f(n) \ge 1$ for $n > k$,
    and so $\P\{N > k\} \le \E[f(N)]$.
    Now, $\E[f(N)] = \lambda^{k+1} / (k+1)!$ via direct calculation or the
    formula for the $k+1$st factorial moment for the Poisson distribution.
\end{proof}
